Computing astrophysical inferences with diffusive nested sampling

### 2014-02-01 ms.tex
Wrote some words

\subsection{MCMC inside nested sampling}

>>>>

\subsection{MCMC inside nested sampling}
The main challenge in Nested Sampling is to generate new points from the
constrained prior distribution $\propto \pi(\pars)\mathds{1}(L(\pars) > L^*)$.
Two popular strategies are in use. The first is to use the remaining ``live
points'', which are known to be above the likelihood threshold $L^*$, to build
an approximation to the constrained prior, which can then be used to generate
a new point via rejection sampling \citep{multinest}.

The second common strategy is to use MCMC. Since the remaining live points are
known to exceed the likelihood threshold, they can be used to initialise an
MCMC run. This strategy is very simple but has known issues.
